Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-12 Article.tex

In more details, and as will be explained in section \ref{sec:model}, we consider agents that, depending on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled).  We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic correlations. With these ingredients, we are able to run simulations and record the different output profiles as timeseries.

>>>>

In more details, and as will be explained in section \ref{sec:model}, we have consider agents that depend on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled). We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic correlations. With these ingredients, we are able to run simulations and record the different output profiles as timeseries.
